### 2019-04-24 manuscript.tex
somthing

\begin{titlepage}
	\centering
	%\includegraphics[width = number\textwidth]{image title}\par\vspace{1cm}}
	%this could be used to add the Aberdeen logo?
	{\scshape\Large The University of Aberdeen \par}
	\vspace{1cm}
	{\huge\bfseries Asymetry and the Absence of Patterns Do Not Encourage Optimal Decisions.\par}
	\vspace{1cm}
	{\Large\itshape Warren James\par}
	\vfill
	Supervised by\par
	Dr.~Amelia \textsc{Hunt}\par
	and\par
	Prof.~Ben \textsc{Tatler}\par
	\textbf{Word Count:} 12755
	\vfill
\end{titlepage}

@@

\paragraph{} We may often find ourselves with multiple tasks to complete but limited resources with which to complete them. For example, with in upcoming exam, students will often have a large amount of material to cover but only a limited amount of time to spend revising the subjects. How a student should divide up their time depends on how well prepared they are. A well prepared student would probably benefit from covering each topic an equal amount as they are already likely to succeed. On the other hand, a poorly prepared student may benefit from spending all their time on a subset ot topics and hope that the topics they revised for come up. %Exams often require that the student has a reasonable level of knowledge about all possible topics that may appear. However, often there can be a wide range of topics that are not always so easy to link and thus appear entirely separate. Some students may struggle with the topics that are going to come up, whereas others might be very confident in their chances of succeeding regardless of what actually appears in the exam questions. For these two hypothetical students, it does not make sense for them to approach these situations with the same strategy. The student that is already fairly confident would benefit more from dividing their time relatively equally across the subjects that may come up because they are already fairly prepared. However, the student with little knowledge may not be able to reach a suitable level of preparedness for the exam if they were to split their time. Instead, for this student, it may be more beneficial to instead be more selective in what they study and primarily focus on one topic in the hope that topic will be in the exam.

\paragraph{} Implementing this logic may seem fairly straightforward; if every task is difficult, it is a good idea to focus on only a subset, whereas when the tasks are straightforward, it makes sense to instead attempt a larger number. However, in tasks that present scenarios in which this logic should be applied,  people demonstrate an inability to switch from attempting both goals in an easy context, to focussing on one when they are both difficult \citep{clarke2015failure,morvan2012human}. By not following this relatively simple logic, the rate of success can fall far below what would be expected should the optimal strategy have been implemented.

\paragraph{} It is assumed by the Expected Utility Theory (EUT) that people generally aim to maximise the utility of their actions; in other words, we tend to choose a course of action that would be most beneficial to us \citep{mongin1997expected}. When faced with uncertain, or risky, prospects, EUT suggests that we should pick the option that would be expected to give the decision maker the greatest rate of return. However, even before considering empirical evidence, it is possible to demonstrate that this theory can become incredibly hard to implement. \cite{BOSSAERTS2017917} discuss a thought experiment about shopping in which a person is expected to enter a shop and select the groceries that fulfil their criteria whilst also offering the maximum value. In their thought experiment, this shop only contains 100 items but this still offers a very large amount of comparisons to be made ($10^{30}$ comparisons). Considering this, it is possible to argue that the EUT is unlikely to explain behaviour very well when it comes to instances where there are a large number of options to choose from.

\paragraph{} As mentioned above, using the EUT can entail some very computationally complex comparisons being required which would simply be beyond the scope of human beings \citep{BOSSAERTS2017917}. However, this does not mean that we can simply say human beings are irrational because we cannot implement this approach all the time. Instead, we must begin to consider that there are limitations to what human beings are able to do \citep{simon1990invariants}. This is the idea of \textit{Bounded Rationality} which posits that these limitations are important to consider when looking at human rationality. Instead of being "objectively optimal", perhaps we are behaving in such a way that accounts for our ability. Making $10^{30}$ comparisons might be simply too daunting and therefore we may instead opt for a much more simple approach.

\paragraph{} When it comes to smaller problems, it is feasible to implement a strategy that compares the expected outcome across multiple choices. However, \cite{KahnemanProspect} present evidence that suggests that this is not the case either. In their work, they presented people with two choices; \textit{Option A} offered participants a $50\%$ chance to win \$1000 and a $50\%$ to win nothing, and \textit{Option B} would give them \$450 for certain. Using the EUT, Option A is the better option as this would on average reward the participant \$500. However, this was not the observed pattern of behaviour for most participants who instead would opt for \textit{Option B}. Perhaps more interestingly, they found that framing problems such as these would result in a shift from the sure option, to the more "risky" option. When framing this decision as being a loss rather than a gain, participants would instead opt for \textit{Option A} which in this context would be the worst option as is offers the greatest average loss. It can be argued that since the choices people make can be altered by simply changing the way a problem is framed, we are not simply comparing options and choosing the one that offers the best outcome \citep{KahnemanChoicesValuseFrames}.

% \subsection*{Cognitive Biases}
% \addcontentsline{toc}{subsection}{Cognitive Biases}
% Not sure if this is entirely needed to be honest...

\paragraph{} The issue with these sorts of tasks is that they are hypothetical \citep{KahnemanProspect}. Participants are supposed to imagine they are in a situation where choosing either option would result in one of the two stated outcomes. The question arises; what if people are put in a situation in which they are making decisions with actual outcomes? Until this point, the tasks considered have been hypothetical and are rarely (if ever) encountered in everyday life. As such, it would make more sense to look at decisions that people make many times a day. One task that fills this criteria is visual search. Whilst looking for something, we often aim to look in the places that are most likely to contain the item of interest. \cite{najemnik2005optimal} suggest that the way in which we scan a visual scene reflects that of an optimal strategy in that we choose to fixate the locations that are most likely to guide us towards the target or offer us the most information. By creating a model that accounted for the underlying statistics of a scene and the limitations of visual acuity, they argued they were able to predict eye movement patterns that closely resembled those of humans. Therefore, they argued that as performance of the ideal observer and human observe were very similar, we may be doing something close to optimal when directing our eye movements to locations within a scene.

\paragraph{} The model presented by \cite{najemnik2005optimal} suggests that humans are able to account for their own limitations and perform a complex task in an almost optimal manner. Should people be able to perform in the task of searching a visual scene optimally, then it should logically follow that doing this in a more simple scenario should also be possible. However, a study by \cite{morvan2012human} appears to demonstrate that this is not the case, and instead people struggle to account for their own visual acuity in order to make a decision that would reap the highest reward.

\paragraph{} The task employed by \cite{morvan2012human} made use of a very simple display containing three boxes; one central with two on either side equidistant from the central box. This distance would change from being very close to being very far apart. Participants were tasked with detecting a target that would appear in either the left or right box (with equal likelihood) at the top or the bottom (again, with equal likelihood) and were tasked to state whether this target was at the top or bottom. Participants were told that they could fixate any of the three boxes displayed on screen but that the target would only ever appear in one of the two flanking boxes. The logic with regards to allocating resources can be applied here; when the boxes are close together (easy), then one should fixate the central box as it is possible to use peripheral vision to see both boxes, however, when they are far apart, one should instead fixate one of the side boxes as visual acuity will drop off in the periphery. Using the knowledge that each there is an equal chance of the target appearing in either box at the top or the bottom, we can see that switching to focussing on one of the side boxes means that accuracy should be $\approx75\%$. Participants should be $100\%$ accurate for their fixated box and, due to chance, be correct $50\%$ of the time for the non-fixated box resulting in an average accuracy of $75\%$. For each participant, visual acuity was tested in order to calculate at what point the participant should have switched from looking in the centre to looking at the side in order to achieve the greatest accuracy.

\paragraph{} The results from \cite{morvan2012human} and the replication by \cite{clarke2015failure} (hereafter referred to as the \textit{Detection Task}) suggested that people were unable to perform this task in such a way that would maximise their success. Participants did not appear to vary their fixation locations as a function of distance which would be expected should they have employed the optimal strategy. These results were also present in two other versions of this task that were carried out by \cite{clarke2015failure}. These other tasks made use of the same problem, but presented in several different ways. Their reason for doing this was to investigate whether this failure to "solve" this problem was specific to eye movements. The first of these three tasks involved participants trying to recall one of two strings of digits that could be short and therefore easy to remember, or long and more difficult to remember (the \textit{Memory Task}). For short sequences, it is easy to recall both and therefore time should be spent on each sequence, whereas when the sequences were long, the entire presentation time should be spent learning one of the sequences. The other involved participants selecting a standing position in order to throw a bean bag into one of two hoops (the \textit{Throwing Task}). Again, the same logic could be applied in that when the hoops were close, one should stand between and equidistant from each hoop, but for larger separations, standing next to one would increase chances of success. In both of these tasks, participants were unable to change their strategy as a function of difficulty thus further replicating these results.

\paragraph{} However, in the last task they used, participants were uniformly able to complete the task using the optimal strategy. This final task (the \textit{Reaching Task}) required participants to select from one of three chairs in order to reach for one of two bean bags that were positioned on a table \citep{clarke2015failure}. The chairs were spaced so that one was in the centre with two at either end of the table. Again, the same strategy should be employed; sit in the centre when the bean bags were close together, but choose one of the side chairs when the distance was large. For the \textit{Reaching Task}, participants simply had to know how far they could reach which is something that would appear to be very easy to estimate due to its more tangible nature. However, the other tasks required an understanding of a more abstract ability.

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be. As it was possible that participants were aware of their own ability but were not using this information, half of the participants were asked to state after having selected somewhere to stand. This was added as a potential prompt for participants to make use of this information which may have potentially improved performance \citep{chang2014self}. The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial, however, did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using knowledge of their ability to accuractely throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the four studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

\subsection*{Probability Matching}
\addcontentsline{toc}{subsection}{Probability Matching}
%This is just a temporary intro to this section that can be edited at any point depening on where it is positioned in the final version
\paragraph{} The first of these factors to be investigated is that of \textit{Probability Matching}. \textit{Probability Matching} is when people select each item based on the probability that it will appear. This is often regarded as a suboptimal behaviour as it does not offer the greatest rate of success \citep{Koehler2010}. An eaxmple of this would be if one was tasked with selecting between two options several times in a row. If option A would reward you 80\% of the time, and option B only 20\% of the time, the best course of action is to pick option A all the time as this would result in an average success rate of 80\%. Whereas trying to match the probabilities by selecting each option in proportion to its likelihood of success would only yield an average success rate of 68\%.

\paragraph{} On face value, this appears to be a misunderstanding of probability. However, if one is able to detect the likelihood of each event occurring, this information can be useful in making decisions about where to direct our efforts. In the original paradigm \citep{clarke2015failure}, each potential target was equally likely to become the actual target. One may compare this to the "\textit{Buridan's Ass}" in which a donkey is equally hungry and thirsty whilst being equidistant from a source of food, and of water. With this in mind, there is no reason to opt for one target over the other as they are both equally attractive. Having two equally likely targets to aim for may have caused participants in \cite{clarke2015failure} to rely more heavily on a centre strategy than they should have given the optimal solution to the task. Committing to one side or the other may have been seen as "too risky" in such an uncertain context and so it may have appeared safer to opt for a more central location.

\paragraph{} One way in which this can be investigated is by introducing a bias for one side to become the target more often than the other. Essentially, this would provide participants with a "pattern" that could be learnt and used to aid them in making a decision. As discussed before, people have a general drive to seek out patterns in order to inform their decisions \citep{yellott1969probability}. This tendency to seek out and exploit patterns can be seen in peoples' tendency to "\textit{Probability Match}" \citep{Koehler2010}. For example, \cite{Koehler2010} conducted a study in which participants had to guess whether a coin had been placed under a red or green cup. Participants were presented with 10 pairs of cups (one red and one green), and were told that for each pair a coin had been placed under either cup. The experimenter told them that they had decided under which cup to place the coin by rolling a 10-sided die with seven green faces and three red faces. The participants then had to produce a list of 10 guesses as to which cup they believed contained the coin. In this case, strictly matching would result in an accuracy of $58\%$, whereas always selecting the most likely option (\textit{maximising}) would result in an average accuracy of $70\%$.

\paragraph{} Clearly maximising produces the more favourable outcome, however in their study \citep{Koehler2010} a minority of participants opted for this strategy (in total, $22\%$ of participants were strict maximisers). The question arises as to why people may be opting for a strategy that does not grant the best chance of success. \cite{Gao2015} argue that by \textit{maximising}, you are accepting that you will make a sure loss for a minority of trials. As such, the only way to negate this sure loss is to predict the sequence accurately. They argue that people instead choose to \textit{probability match} as this will allows for a very slim chance to earn 100\% of the reward \citep{Gao2015}.

\paragraph{} To investigate the idea that matching is the result of attempting to be $100\%$ accurate, \cite{Gao2015} conducted a study in which participants predicted whether a red or green light would be displayed. One of the lights would appear $80\%$ of the time and the other only $20\%$ of the time. In the experiment, participants were given the chance to earn a bonus reward if they managed to get a certain accuracy level over 5 trials. They were either told the bonus would be earned if they were $100\%$, $80\%$, or $60\%$ accurate. The hypothesis was that when participants were told the bonus would be awarded for achieving $100\%$ accuracy, then they should observe a greater tendency to opt for a matching strategy.

\paragraph{} This is what they observed; participants in the $100\%$ condition did have a higher rate of strictly matching. They suggested that by giving participants the goal of aiming to be $100\%$ accurate, participants began to focus on overall accuracy rather than treating each trial as independent of the others, something they argue is more likely to result in matching behaviour \citep{Gao2015}. Thus, they argue that the tendency to engage in matching behaviour is similar to the idea of avoiding loss \citep{KahnemanProspect}. By always choosing the more likely option, it is possible to view this as accepting some sure losses.

\paragraph{} This idea can be linked to the paper by \cite{clarke2015failure} in which the probability for each potential target was $50\%$. It is possible that participants would view choosing to focus their attention exclusively on a single option as being too risky due to the other option becoming a sure loss. By remaining somewhat central, there is still a small chance to succeed should either target be selected, albeit a very small chance. By introducing a bias to one side, this may push the more likely option to be a sufficiently attractive option so as to become a more viable option. Further, by adding in a bias for one option to be more likely, this may cater to a natural tendency to seek out and attempt to exploit patterns \citep{gaissmaier2008smart,yellott1969probability}.

@@

\paragraph{} \cite{wolford2004searching} presented participants with the task of guessing whether a target would appear in the upper or lower portion of a computer screen. One of these locations would be biased to contain the target $75\%$ of the time, and the other would only contain the target $25\%$ of the time. Some participants would simply carry out this task as a control group. Others would have to perform one of two distractor tasks. The task they opted for to occupy the left hemisphere involved remembering the last three digits they had seen. Before each trial, a digit would appear, and at random points during the block they would be asked to recall the most recent three digits that had been presented. Additionally, other participants were presented with a 6 sided polygon and were asked to recall whether this was the same or different to the one they had seen previously. Participants performing the distractor tasks were told that inaccuracies would result in a reduction of their reward. Their results suggested that by giving participants a task that occupied the left hemisphere, they began to approach a maximising strategy. The results of this study suggest that disrupting the search for patterns had pushed these participants to behave in a more "optimal" manner.

@@

\subsection*{Patterns}
\addcontentsline{toc}{subsection}{Patterns}

\paragraph{} As mentioned above, one potential explanation as to why people opt for a stratey of probability matching may come from the search for patterns \citep{yellott1969probability}. This predisposition to search for patterns has been implicated as a reason why people fail to find more appropriate, and optimal solutions to  certain problems \citep{wolford2004searching}.  %The above sections have suggested ways in which the symmetry of the problem can be broken in order to cause one side to be more attractive than the other. However, one fundamental issue with this has already been mentioned; the pursuit of patterns \citep{wolford2004searching}. This predisposition to search for patterns is evident in the way in which it can interrupt the use of more sensible strategies \citep{wolford2004searching}, and also means we can "detect" patterns that simply do not exist \cite{yellott1969probability}. An experiment in the paper by \cite{yellott1969probability} asks people to make a simple guess as to whether one of two options will appear next. Unbeknownst to them, the option they pick will always be the correct answer. After having carried out this experiment, the participants were asked to explain how they made their choices and whether they had detected a pattern. Despite none existing, participants were able to produce some fairly elaborate patterns that also matched onto the choices they had made during the task.

\paragraph{} With this comes the question, are participants trying to detect a pattern when completing the tasks of \cite{clarke2015failure}? Within a task such as this, it is often difficult to persuade participants that the sequence is entirely random as people generally have a misunderstanding of what \textit{randomness} is \citep{Ayton2004}. This can be seen in two biases that people tend to possess. The \textit{Gambler's Fallacy} is the often erroneous belief that the next event has a higher chance to not be the same as the previous. For example, seeing a coin flipped 5 times and seeing it land showing heads after every flip does not increase the chances that the next flip will result in a tails, however, falling for the \textit{Gambler's Fallacy} would mean that people are more likely to suggest that tails will come up on the next throw. The other is the \textit{Hot-Hand Illusion} which is essentially the opposite. Instead of thinking that things will change, this is the idea that things should remain stable and so a long sequence of heads would increase (again, erroneously) the odds that the next event will also be heads.

>>>>

\begin{titlepage}
	\centering
	%\includegraphics[width = number\textwidth]{image title}\par\vspace{1cm}}
	%this could be used to add the Aberdeen logo?
	%{\scshape\Large The University of Aberdeen \par}
	%\vspace{1cm}
	{\huge\bfseries Asymetry and the Absence of Patterns Do Not Encourage Optimal Decisions.\par}
	\vspace{1cm}
	Warren \textsc{James}, \par
	Dr.~Amelia \textsc{Hunt},\par
	and\par
	Dr.~Alasdair \textsc{Clarke}
	\vfill
\end{titlepage}

@@

\paragraph{} We may often find ourselves with multiple tasks to complete but limited resources with which to complete them. For example, with in upcoming exam, students will often have a large amount of material to cover but only a limited amount of time to spend revising the subjects. How a student should divide up their time depends on how well prepared they are. A well prepared student would probably benefit from covering each topic an equal amount as they are already likely to succeed. On the other hand, a poorly prepared student may benefit from spending all their time on a subset of topics and hope that the topics they revised for come up. %Exams often require that the student has a reasonable level of knowledge about all possible topics that may appear. However, often there can be a wide range of topics that are not always so easy to link and thus appear entirely separate. Some students may struggle with the topics that are going to come up, whereas others might be very confident in their chances of succeeding regardless of what actually appears in the exam questions. For these two hypothetical students, it does not make sense for them to approach these situations with the same strategy. The student that is already fairly confident would benefit more from dividing their time relatively equally across the subjects that may come up because they are already fairly prepared. However, the student with little knowledge may not be able to reach a suitable level of preparedness for the exam if they were to split their time. Instead, for this student, it may be more beneficial to instead be more selective in what they study and primarily focus on one topic in the hope that topic will be in the exam.

\paragraph{} Implementing this logic may seem fairly straightforward; if every task is difficult, it is a good idea to focus on only a subset, whereas when the tasks are straightforward, it makes sense to instead attempt a larger number. However, in tasks that present scenarios in which this logic should be applied,  people demonstrate an inability to switch from attempting both goals in an easy context, to focussing on one when they are both difficult \citep{clarke2015failure,morvan2012human}. By not following this relatively simple logic, the rate of success can fall far below that which would be expected should the optimal strategy have been implemented.

\paragraph{} Some theories assume that people generally aim to make decisions that offer the greatest expected utility \citep{mongin1997expected}. However, problems can become intractable as the number of possible outcomes to compare grows \citep[see ][ for a discussion of this]{BOSSAERTS2017917}. Therefore, when thinking of optimal decisions, one must take into account the limitations of the indivdual. This is termed Bounded Rationality \citep{simon1990invariants} and posits that people do make optimal decisions given some limitations.

%\paragraph{} It is assumed by the Expected Utility Theory (EUT) that people generally aim to maximise the utility of their actions; in other words, we tend to choose a course of action that would be most beneficial to us \citep{mongin1997expected}. When faced with uncertain, or risky, prospects, EUT suggests that we should pick the option that would be expected to give the decision maker the greatest rate of return. However, even before considering empirical evidence, it is possible to demonstrate that this theory can become incredibly hard to implement. \cite{BOSSAERTS2017917} discuss a thought experiment about shopping in which a person is expected to enter a shop and select the groceries that fulfil their criteria whilst also offering the maximum value. In their thought experiment, this shop only contains 100 items but this still offers a very large amount of comparisons to be made ($10^{30}$ comparisons). Considering this, it is possible to argue that the EUT is unlikely to explain behaviour very well when it comes to instances where there are a large number of options to choose from.

%\paragraph{} As mentioned above, using the EUT can entail some very computationally complex comparisons being required which would simply be beyond the scope of human beings \citep{BOSSAERTS2017917}. However, this does not mean that we can simply say human beings are irrational because we cannot implement this approach all the time. Instead, we must begin to consider that there are limitations to what human beings are able to do \citep{simon1990invariants}. This is the idea of \textit{Bounded Rationality} which posits that these limitations are important to consider when looking at human rationality. Instead of being "objectively optimal", perhaps we are behaving in such a way that accounts for our ability. Making $10^{30}$ comparisons might be simply too daunting and therefore we may instead opt for a much more simple approach.

\paragraph{} When it comes to smaller problems, it is feasible to implement a strategy that compares the expected outcome across multiple choices. However, \cite{KahnemanProspect} present evidence that suggests that this is not the case either. In their work, they presented people with two choices; \textit{Option A} offered participants a $50\%$ chance to win \$1000 and a $50\%$ to win nothing, and \textit{Option B} would give them \$450 for certain. Using the EUT, Option A is the better option as this would on average reward the participant \$500. However, this was not the observed pattern of behaviour for most participants who instead would opt for \textit{Option B}. Perhaps more interestingly, they found that framing problems such as these would result in a shift from the sure option, to the more "risky" option. When framing this decision as being a loss rather than a gain, participants would instead opt for \textit{Option A} which in this context would be the worst option as it offers the greatest average loss. It can be argued that since the choices people make can be altered by simply changing the way a problem is framed, we are not simply comparing options and choosing the one that offers the best outcome \citep{KahnemanChoicesValuseFrames}, and instead we are incorporating information that is not relevant to the decision being made.

\paragraph{} The issue with these sorts of tasks is that they are hypothetical \citep{KahnemanProspect}. Participants are supposed to imagine they are in a situation where choosing either option would result in one of the two stated outcomes. The question arises; what if people are put in a situation in which they are making decisions with actual outcomes? Until this point, the tasks considered have been hypothetical and are rarely (if ever) encountered in everyday life. As such, it would make more sense to look at decisions that people make many times a day.

\paragraph{} One task that fills this criteria is visual search. Whilst looking for something, we often aim to look in the places that are most likely to contain the item of interest. \cite{najemnik2005optimal} suggest that the way in which we scan a visual scene reflects that of an optimal strategy in that we choose to fixate the locations that are most likely to guide us towards the target or offer us the most information. By creating a model that accounted for the underlying statistics of a scene and the limitations of visual acuity, they argued they were able to predict eye movement patterns that closely resembled those of humans. Therefore, they argued that as performance of the ideal observer and human observe were very similar, we may be doing something close to optimal when directing our eye movements to locations within a scene.

\paragraph{} The model presented by \cite{najemnik2005optimal} suggests that humans are able to account for their own limitations and perform a complex task in an almost optimal manner. Should people be able to perform in the task of searching a visual scene optimally, then it should logically follow that doing this in a more simple scenario should also be possible. However, a study by \cite{morvan2012human} appears to demonstrate that this is not the case. Instead people struggle to account for their own visual acuity in order to make a decision that would reap the highest reward.

\paragraph{} The task employed by \cite{morvan2012human} made use of a very simple display containing three boxes; one central with two on either side equidistant from the central box. This distance would change from being very close to being very far apart. Participants were tasked with detecting a target that would appear in either the left or right box (with equal likelihood) at the top or the bottom (again, with equal likelihood) and were tasked to state whether this target was at the top or bottom. Participants were told that they could fixate any of the three boxes displayed on screen but that the target would only ever appear in one of the two flanking boxes. The logic with regards to allocating resources can be applied here; when the boxes are close together (easy), then one should fixate the central box as it is possible to use peripheral vision to see both boxes, however, when they are far apart, one should instead fixate one of the side boxes as visual acuity will drop off in the periphery. Using the knowledge that there is an equal chance of the target appearing in either box at the top or the bottom, we can see that switching to focussing on one of the side boxes means that accuracy should be $\approx75\%$. Participants should be $100\%$ accurate for their fixated box and, due to chance, be correct $50\%$ of the time for the non-fixated box. For each participant, visual acuity was tested in order to calculate at what point the participant should have switched from looking in the centre, to looking at the side in order to achieve the greatest accuracy.

\paragraph{} The results from \cite{morvan2012human} and the replication by \cite{clarke2015failure} suggest that people were unable to perform this task in such a way that would maximise their chance success. Participants did not appear to vary their fixation locations as a function of distance which would be expected should they have employed the optimal strategy. These results were also present in two other versions of this task that were carried out by \cite{clarke2015failure}. These other tasks made use of the same problem, but presented in several different ways. Their reason for doing this was to investigate whether this failure to "solve" this problem was specific to eye movements. One task involved being presented with two strings of digits and then being prompted to recall one of them, the other task involved throwing bean bags into one of two hoops. Participants, again, failed to make decisions that would optimise their chance of success.

% The first of these three tasks involved participants trying to recall one of two simultaneously presented strings of digits that could be short and therefore easy to remember, or long and more difficult to recall. For short sequences, it is easy to remember both and therefore time should be spent on each sequence, whereas when the sequences were long, the entire presentation time should be spent learning one of the sequences. The other involved participants selecting a standing position in order to throw a bean bag into one of two hoops. Again, the same logic could be applied in that when the hoops were close, one should stand between and equidistant from each hoop, but for larger separations, standing next to one would increase chances of success. In both of these tasks, participants were unable to change their strategy as a function of difficulty thus further replicating these results.

\paragraph{} However, in the last task they used, participants were uniformly able to complete the task using the optimal strategy. This final task required participants to select from one of three chairs in order to reach for one of two bean bags that were positioned on a table \citep{clarke2015failure}. The chairs were spaced so that one was in the centre with two at either end of the table. Again, the same strategy should be employed; sit in the centre when the bean bags were close together, but choose one of the side chairs when the distance was large. For the \textit{Reaching Task}, participants simply had to know how far they could reach which is something that would appear to be very easy to estimate due to its more tangible nature. However, the other tasks required an understanding of a more abstract ability.

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be.  The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial, however, did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using knowledge of their ability to accuractely throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the four studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

% As it was possible that participants were aware of their own ability but were not using this information, half of the participants were asked to state after having selected somewhere to stand. This was added as a potential prompt for participants to make use of this information which may have potentially improved performance \citep{chang2014self}.

\subsection*{Probability Matching}
\addcontentsline{toc}{subsection}{Probability Matching}
%This is just a temporary intro to this section that can be edited at any point depening on where it is positioned in the final version
\paragraph{} The first of these factors to be investigated is that of \textit{Probability Matching}. This is often regarded as a suboptimal behaviour as it does not offer the greatest rate of success \citep{Koehler2010}. An eaxmple of this would be if one was tasked with selecting between two options several times in a row. If option A would reward you 80\% of the time, and option B only 20\% of the time. The best course of action is to pick option A every time as this would result in an average success rate of 80\%. Whereas trying to match the probabilities by selecting each option in proportion to its likelihood of success would only yield an average success rate of 68\%.

\paragraph{} On face value, this appears to be a misunderstanding of probability. However, if one is able to detect the likelihood of each event occurring, this information can be useful in making decisions about where to direct our efforts. For example, there could be a pattern present that would be beneficial to exploit \citep{wolford2004searching}. In the original paradigm \citep{clarke2015failure}, each potential target was equally likely to become the actual target. One may compare this to the "\textit{Buridan's Ass}" in which a donkey is equally hungry and thirsty whilst being equidistant from a source of food, and of water. Which should the Donkey approach first? There is no reason to opt for one target over the other as they are both equally attractive. Having two equally likely targets to aim for may have caused participants in \cite{clarke2015failure} to rely more heavily on a centre strategy than they should have given the optimal solution to the task. Committing to one side or the other may have been seen as "too risky" in such an uncertain context and so it may have appeared safer to opt for a more central location. %\textbf{\textit{Not sure I like this... Probably change this to be about looking for other sources of information?}}

\paragraph{} One way in which this can be investigated is by introducing a bias for one side to become the target more often than the other. Essentially, this would provide participants with a "pattern" that could be learnt and used to aid them in making a decision. People have a general drive to seek out patterns in order to inform their decisions \citep{yellott1969probability}. This tendency to seek out and exploit patterns can be seen in peoples' tendency to "\textit{Probability Match}" \citep{Koehler2010} in which a large portion of participants engaged in probability matching. %, some still selecting the least likely option on some amount of trials, and a small minority engaged in strict \textit{maximising}.

% For example, \cite{Koehler2010} conducted a study in which participants had to guess whether a coin had been placed under a red or green cup. Participants were presented with 10 pairs of cups (one red and one green), and were told that for each pair a coin had been placed under either cup. The experimenter told them that they had decided under which cup to place the coin by rolling a 10-sided die with seven green faces and three red faces. The participants then had to produce a list of 10 guesses as to which cup they believed contained the coin. In this case, strictly matching would result in an accuracy of $58\%$, whereas always selecting the most likely option (\textit{maximising}) would result in an average accuracy of $70\%$.

\paragraph{} The question arises as to why people may be opting for a strategy that does not grant the best chance of success. \cite{Gao2015} argue that by \textit{Maximising}, you are accepting that you will make a sure loss for a minority of trials. As such, the only way to negate this sure loss is to predict the sequence accurately. They argue that people instead choose to Probability Match as this will allows for a very slim chance to earn 100\% of the reward \citep{Gao2015}.

%\paragraph{} To investigate the idea that matching is the result of attempting to be $100\%$ accurate, \cite{Gao2015} conducted a study in which participants predicted whether a red or green light would be displayed. One of the lights would appear $80\%$ of the time and the other only $20\%$ of the time. In the experiment, participants were given the chance to earn a bonus reward if they managed to get a certain accuracy level over 5 trials. They were either told the bonus would be earned if they were $100\%$, $80\%$, or $60\%$ accurate. The hypothesis was that when participants were told the bonus would be awarded for achieving $100\%$ accuracy, then they should observe a greater tendency to opt for a matching strategy.

%\paragraph{} This is what they observed; participants in the $100\%$ condition did have a higher rate of strictly matching. They suggested that by giving participants the goal of aiming to be $100\%$ accurate, participants began to focus on overall accuracy rather than treating each trial as independent of the others, something they argue is more likely to result in matching behaviour \citep{Gao2015}. Thus, they argue that the tendency to engage in matching behaviour is similar to the idea of avoiding loss \citep{KahnemanProspect}. By always choosing the more likely option, it is possible to view this as accepting some sure losses.

\paragraph{} This idea can be linked to the paper by \cite{clarke2015failure} in which the probability for each potential target was $50\%$. It is possible that participants would view choosing to focus their attention exclusively on a single option as being too risky due to the other option becoming a sure loss. By rarely committing to one option, there is still a small chance to succeed should either target be selected. By introducing a bias to one side, this may push the more likely option to be a sufficiently attractive option so as to become a more viable option. Further, by adding in a bias for one option to be more likely, this may cater to a natural tendency to seek out, and attempt to exploit, patterns \citep{gaissmaier2008smart,yellott1969probability}.

@@

%\paragraph{} \cite{wolford2004searching} presented participants with the task of guessing whether a target would appear in the upper or lower portion of a computer screen. One of these locations would be biased to contain the target $75\%$ of the time, and the other would only contain the target $25\%$ of the time. Some participants would simply carry out this task as a control group. Others would have to perform one of two distractor tasks. The task they opted for to occupy the left hemisphere involved remembering the last three digits they had seen. Before each trial, a digit would appear, and at random points during the block they would be asked to recall the most recent three digits that had been presented. Additionally, other participants were presented with a 6 sided polygon and were asked to recall whether this was the same or different to the one they had seen previously. Participants performing the distractor tasks were told that inaccuracies would result in a reduction of their reward. Their results suggested that by giving participants a task that occupied the left hemisphere, they began to approach a maximising strategy. The results of this study suggest that disrupting the search for patterns had pushed these participants to behave in a more "optimal" manner.

@@

%\subsection*{Patterns}
%\addcontentsline{toc}{subsection}{Patterns}

%\paragraph{} As mentioned above, one potential explanation as to why people opt for a stratey of probability matching may come from the search for patterns \citep{yellott1969probability}. This predisposition to search for patterns has been implicated as a reason why people fail to find more appropriate, and optimal solutions to  certain problems \citep{wolford2004searching}.  %The above sections have suggested ways in which the symmetry of the problem can be broken in order to cause one side to be more attractive than the other. However, one fundamental issue with this has already been mentioned; the pursuit of patterns \citep{wolford2004searching}. This predisposition to search for patterns is evident in the way in which it can interrupt the use of more sensible strategies \citep{wolford2004searching}, and also means we can "detect" patterns that simply do not exist \cite{yellott1969probability}. An experiment in the paper by \cite{yellott1969probability} asks people to make a simple guess as to whether one of two options will appear next. Unbeknownst to them, the option they pick will always be the correct answer. After having carried out this experiment, the participants were asked to explain how they made their choices and whether they had detected a pattern. Despite none existing, participants were able to produce some fairly elaborate patterns that also matched onto the choices they had made during the task.

%\paragraph{} With this comes the question, are participants trying to detect a pattern when completing the tasks of \cite{clarke2015failure}? Within a task such as this, it is often difficult to persuade participants that the sequence is entirely random as people generally have a misunderstanding of what \textit{randomness} is \citep{Ayton2004}. This can be seen in two biases that people tend to possess. The \textit{Gambler's Fallacy} is the often erroneous belief that the next event has a higher chance to not be the same as the previous. For example, seeing a coin flipped 5 times and seeing it land showing heads after every flip does not increase the chances that the next flip will result in a tails, however, falling for the \textit{Gambler's Fallacy} would mean that people are more likely to suggest that tails will come up on the next throw. The other is the \textit{Hot-Hand Illusion} which is essentially the opposite. Instead of thinking that things will change, this is the idea that things should remain stable and so a long sequence of heads would increase (again, erroneously) the odds that the next event will also be heads.

%\paragraph{} \cite{KAHNEMAN1972430} suggest that the \textit{Gambler's Fallacy} is a result of us expecting to see something that is representative of the underlying probability. In essence, we expect the short-term to behave in the same expected way to the long-term. With enough coin flips, we should begin to see proportions that reflect the random nature of a coin flip. This is not the same for much shorter sequences, and as such, this may be where the \textit{Gambler's Fallacy} comes from. We may tend to believe that a short sequence should also match the underlying probabilities in the same way a long sequence would. However, this argument does not explain how the \textit{Hot-Hand Illusion} can arise; if we believe that all sequences should closely resemble the expected probability of each event's success, why would we expect there to be long streaks? \cite{Ayton2004} suggest that these phenomena emerge from slightly different contexts.
